Containers and R---the Rockerverse and beyond

### 2019-11-06 manuscript.Rmd

# R Packages

## Packages for automation and packaging [@nuest]

- [`containerit`](https://github.com/o2r-project/containerit/)
- [`dockertest`](https://github.com/traitecoevo/dockertest/)

### liftr

@@

## Packages for control and provisioning [@nuest, @richfitz, @rcannood]

- [`stevedore`](https://github.com/richfitz/stevedore)
- [`babelwhale`](https://cran.r-project.org/web/packages/babelwhale/index.html): Running a Docker from R with Singularity or Docker as back-end. This is really useful in HPC environments where a user might not have root access but is able to install Singularity instead of Docker. [@rcannood]
- [`docker`](https://bhaskarvk.github.io/docker/)
- `RSelenium`
- [`googleComputeEngineR`](https://cloudyr.github.io/googleComputeEngineR/) (function `docker_run`)
  - I don't think `docker_run` is main focus for containers for this package, its more how it uses Docker to launch custom environments that can be templated (e.g. rstudio, shiny etc.) and for parrallisation e.g. `library(future)`  using GCE VMs as endpoints. [@MarkEdmondson1234]
- [`analogsea`](https://github.com/sckott/analogsea)
- [`harbor`](https://github.com/wch/harbor/)
- [`dockermachine`](https://github.com/cboettig/dockermachine)

>>>>

# R Packages
<!-- from packages closer to Docker to second level packages to more complex ones -->

## Clients
<!-- first order packages, talking directyl to Docker -->

- [`stevedore`](https://github.com/richfitz/stevedore)
- [`docker`](https://bhaskarvk.github.io/docker/)
- [`harbor`](https://github.com/wch/harbor/)
- [`dockermachine`](https://github.com/cboettig/dockermachine)

## Capture and create environments [@nuest]
<!-- second order packages -->

- [`dockerfiler`](https://github.com/ColinFay/dockerfiler/)
- [`containerit`](https://github.com/o2r-project/containerit/)
- [`dockertest`](https://github.com/traitecoevo/dockertest/)

@@
